---
output: rmarkdown::github_document
---

# varmint

Retrieve Content from and Interact with 'Gopher' Servers

## Description

The 'Gopher' protocol is a 'TCP/IP' application layer protocol
designed for distributing, searching, and retrieving documents over the 
Internet. The 'Gopher' protocol was strongly oriented towards a menu-document 
design and presented an alternative to the World Wide Web in its early 
stages, but ultimately 'Hypertext Transfer Protocol' ('HTTP') became the 
dominant protocol. The 'Gopher' ecosystem is often regarded as the effective
predecessor of the 'World Wide Web'. Tools are provided to interact with
and retrieve content from 'Gopher' servers.

## What's Inside The Tin

The following functions are implemented:

- `gopher`:	Fetch a resource using the gopher protocol
- `g_content`:	Retrieve the content portion of a gopher response

## TODO

- better handling of the `url` parameter to `gopher()`
- handle `URL` selectors
- handle content types
- console gopher client
- Shiny gopher client

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/varmint")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(varmint)
library(tidyverse)

# current verison
packageVersion("varmint")
```

### Take a peek at one of the only remaining Gopher servers in existence:

```{r}
x <- gopher("gopher.floodgap.com") 
```

```{r}
str(x)
```

```{r}
x
```

```{r}
g_content(x, TRUE) %>% 
  print(n = 20)
```

### See some other servers

```{r}
x1 <- gopher("gopher://gopher.floodgap.com", "/new") 
```

```{r}
x1
```

```{r}
g_content(x1, TRUE) %>% 
  print(n = 20)
```

### Check out the Veronica menu

```{r}
x2 <- gopher("gopher://gopher.floodgap.com", "/v2") 
```

```{r}
x2
```

```{r}
g_content(x2, TRUE) %>% 
  print(n = 20)
```

### Search for some XKCD comics

```{r}
x3 <- gopher("gopher://gopher.floodgap.com", "/v2/vs", "xkcd")
```

```{r}
x3
```

```{r}
g_content(x3, TRUE) %>% 
  filter(item_type_descr == "info")
```

```{r}
g_content(x3, TRUE) %>% 
  filter(item_type_descr == "menu")
```
